The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-18 paper.tex
Added syncope section

So far, I have employed the {\sc Sonority Angle} metric purely in the analysis of epenthetic processes. However, there are other possible applications.

@@

\ex. \a. Syncope allowed when rising sonority cluster is created
     \a. \textipa{Ev@ri} $\sim$ \textipa{Evri} `every'
     \b. \textipa{mEm@ri} $\sim$ \textipa{mEmri} `memory'
     \z.
     \b. Syncope disallowed when level or falling sonority cluster would be created
     \a. \textipa{pIk@tIN} $\sim$ \textipa{pIktIN} `picketing'
     \b. \textipa{k@p\ae s@ti} $\sim$ \textipa{k@p\ae sti} `capacity'
     \z.
     \citep{hooper.1978}, cited in \citep{flemming.2008}

On the other hand, syncope in Hebrew (and others?) is said to work according to the principles of Syllable Contact:

\ex. TODO: Hebrew etc examples

More work needs to be done to reconcile these two.

>>>>

So far, I have employed the {\sc Sonority Angle} metric purely in the analysis of sonority-driven epenthesis. However, there are other possible applications.

@@

\ex. \a. Syncope allowed when rising sonority cluster is created
     \a. \textipa{Ev@ri} $\sim$ \textipa{Evri} `every'
     \b. \textipa{mEm@ri} $\sim$ \textipa{mEmri} `memory'
     \z.
     \b. Syncope disallowed when level or falling sonority cluster would have been created
     \a. \textipa{pIk@tIN} $\sim$ \textipa{pIktIN} `picketing'
     \b. \textipa{k@p\ae s@ti} $\sim$ \textipa{k@p\ae sti} `capacity'
     \z.
     (Data from \citep{hooper.1978}, cited in \citep{flemming.2008})

On the other hand, syncope in Hebrew \citep{landau.1997}, Lushootseed \citep{urbanczyk.1996} and Mantuan \citep{miglio.1998} are said to work according to the principles of Syllable Contact:

\ex. \a. Syncope allowed when falling sonority cluster is created
     \ag. \v{s}om\'er-et + ot\'o $\rightarrow$ \v{s}om\'eretot\`o (no deletion) / \v{s}om\'ertot\`o \\
          keep-3SgFem + it \\
     \bg. kib\'el + ot\'ax $\rightarrow$ kilb\'eltax \\
          accept.3SgMasc + you \\
     \z.
     \b. Syncope disallowed when rising sonority cluster would have been created
     \ag. hev\'e-tem + ot\'o $\rightarrow$ hev\'etemot\`o (no deletion) / *hev\'etmot\`o \\
          bring-2pl + it \\
     \bg. xa\v{s}av + al\'av $\rightarrow$ *xa\v{s}\'avlav \\
          think.3SgMasc + about.him \\
     \z.
     (Data from \citep{landau.1997})

More work needs to be done to reconcile these two types of sonority-driven syncope.
